### 2009-08-05 doc/latex/sort_8cpp.tex
doxygen documentation as of now

\hypertarget{sort_8hpp}{
\section{cowichan\_\-openmp/sort.hpp File Reference}
\label{sort_8hpp}\index{cowichan\_\-openmp/sort.hpp@{cowichan\_\-openmp/sort.hpp}}
}
Sorting algorithms that use OpenMP.

{\tt \#include \char`\"{}cowichan\_\-openmp.hpp\char`\"{}}\par
\subsection*{Namespaces}
\begin{CompactItemize}
\item 
namespace \hyperlink{namespacecowichan__openmp}{cowichan\_\-openmp}
\begin{CompactList}\small\item\em Additional classes and functions specific to openmp implementation. \item\end{CompactList}

\end{CompactItemize}
\subsection*{Defines}
\begin{CompactItemize}
\item 
\#define \hyperlink{sort_8hpp_b3aee1394b5864d458c40b7878acbe83}{QUICK\_\-SORT\_\-CUTOFF}~100
\item 
\#define \hyperlink{sort_8hpp_66832e055934d011da279261bcfafdd1}{QUICK\_\-SORT\_\-TASK\_\-CUTOFF}~1000
\end{CompactItemize}
\subsection*{Functions}
\begin{CompactItemize}
\item 
void \hyperlink{namespacecowichan__openmp_9cbb3540b84f4e051f072a08c2c1d5db}{cowichan\_\-openmp::histogram\_\-sort} (\hyperlink{class_weighted_point}{WeightedPointVector} vector, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} len)
\item 
void \hyperlink{namespacecowichan__openmp_64208258cab6e46db879b46b40581134}{cowichan\_\-openmp::quick\_\-sort} (\hyperlink{class_weighted_point}{WeightedPointVector} vector, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} len)
\item 
\hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} \hyperlink{namespacecowichan__openmp_2733c307de545e237e020a1f166850c5}{cowichan\_\-openmp::quick\_\-sort\_\-partition} (\hyperlink{class_weighted_point}{WeightedPointVector} vector, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} len, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} pivotIndex)
\end{CompactItemize}

\label{_details}
\hypertarget{_details}{}
\subsection{Detailed Description}
Sorting algorithms that use OpenMP.

Two algorithms are included: \begin{enumerate}
\item Parallel Histogram Sort - similar to bucket sort, but does not require additional space for buckets (in-place).  \item Parallel Quick Sort - requires OpenMP 3.0 \end{enumerate}

\subsection{Define Documentation}
\hypertarget{sort_8hpp_b3aee1394b5864d458c40b7878acbe83}{
\index{sort.hpp@{sort.hpp}!QUICK\_\-SORT\_\-CUTOFF@{QUICK\_\-SORT\_\-CUTOFF}}
\index{QUICK\_\-SORT\_\-CUTOFF@{QUICK\_\-SORT\_\-CUTOFF}!sort.hpp@{sort.hpp}}
\subsubsection[{QUICK\_\-SORT\_\-CUTOFF}]{\setlength{\rightskip}{0pt plus 5cm}\#define QUICK\_\-SORT\_\-CUTOFF~100}}
\label{sort_8hpp_b3aee1394b5864d458c40b7878acbe83}

Quick sort cutoff (becomes insertion sort) - must be $>$ 1 \hypertarget{sort_8hpp_66832e055934d011da279261bcfafdd1}{
\index{sort.hpp@{sort.hpp}!QUICK\_\-SORT\_\-TASK\_\-CUTOFF@{QUICK\_\-SORT\_\-TASK\_\-CUTOFF}}
\index{QUICK\_\-SORT\_\-TASK\_\-CUTOFF@{QUICK\_\-SORT\_\-TASK\_\-CUTOFF}!sort.hpp@{sort.hpp}}
\subsubsection[{QUICK\_\-SORT\_\-TASK\_\-CUTOFF}]{\setlength{\rightskip}{0pt plus 5cm}\#define QUICK\_\-SORT\_\-TASK\_\-CUTOFF~1000}}
\label{sort_8hpp_66832e055934d011da279261bcfafdd1}

Parallel sort cutoff (no more tasks generated).

>>>>

\hypertarget{sort_8cpp}{
\section{cowichan\_\-openmp/sort.cpp File Reference}
\label{sort_8cpp}\index{cowichan\_\-openmp/sort.cpp@{cowichan\_\-openmp/sort.cpp}}
}
Implementation of OpenMP sorting algorithms.

{\tt \#include \char`\"{}sort.hpp\char`\"{}}\par
\subsection*{Namespaces}
\begin{CompactItemize}
\item 
namespace \hyperlink{namespacecowichan__openmp}{cowichan\_\-openmp}
\begin{CompactList}\small\item\em Additional classes and functions specific to openmp implementation. \item\end{CompactList}

\end{CompactItemize}
\subsection*{Functions}
\begin{CompactItemize}
\item 
void \hyperlink{namespacecowichan__openmp_9cbb3540b84f4e051f072a08c2c1d5db}{cowichan\_\-openmp::histogram\_\-sort} (\hyperlink{class_weighted_point}{WeightedPointVector} vector, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} len)
\item 
void \hyperlink{namespacecowichan__openmp_64208258cab6e46db879b46b40581134}{cowichan\_\-openmp::quick\_\-sort} (\hyperlink{class_weighted_point}{WeightedPointVector} vector, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} len)
\item 
\hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} \hyperlink{namespacecowichan__openmp_2733c307de545e237e020a1f166850c5}{cowichan\_\-openmp::quick\_\-sort\_\-partition} (\hyperlink{class_weighted_point}{WeightedPointVector} vector, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} len, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} pivotIndex)
\end{CompactItemize}

\label{_details}
\hypertarget{_details}{}
\subsection{Detailed Description}
Implementation of OpenMP sorting algorithms.
